\input{AufgabenblattPreambel}
\usepackage{amsmath}
\begin{document}
\begin{Aufgabenblatt}{5}{08.07.2009}{20.07.2009}


\begin{Aufgabe}[Text Line Segmentation]{}
  A common method for text line segmentation is upper contour segmentation. The
  upper contour is the y-coordinates of the uppermost edge of a
  character. Segmentation is performed by looking for local minima in the upper
  contour and cutting apart characters at those locations. Implement upper
  contour segmentation. Generate both a color segmentation of the binary input
  image and a list of isolated character images. You can use the Text Line
  Segmentation worksheet as an example. 

  A collection of text line images is present in lines.tgz


  Be sure to create non-trivial test cases and examples that demonstrate that
  your code actually works as expected.
\end{Aufgabe}

\begin{Aufgabe}[Weighted Finite State Acceptors]{}
  Please have a look at the worksheet on Weighted Finite State Acceptors. Based
  on the class defined in that worksheet, implement two functions:
  \begin{itemize}
  \item A $compose(u,v)$ that composes to WFSAs. That is, if
    (string,weight1)$\in u$ and (string,weight2) $\in v$, the result of compose
    should contain (string,weight1+weight2).
  \item A bestpath($u$) function that, given a WFSA, computes a (string,weight)
    pair such that the weight is lower than that of any other string in $u$.
  \end{itemize}

  Be sure to create non-trivial test cases and examples that demonstrate that
  your code actually works as expected.
\end{Aufgabe}

\end{Aufgabenblatt}
\end{document}

\end{Aufgabe}

